%------------------------
% Resume Template
% Author : Mohammad Abdullah Al Mamun
% Github : https://github.com/Mamunia
%------------------------

\documentclass[letterpaper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multibib}
\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
%\fancyfoot{} %when no page numbering needed
%\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\color{black}
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\renewcommand{\labelitemii}{$\circ$}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Huge \scshape Tai-Yu Chen} \\ \vspace{1pt}
    %\small \textit{unknown} \\
    \href{mailto:taiyuchen33@gmail.com}{\underline{taiyuchen33@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/taiyuchen33/}{\underline{linkedin.com/in/taiyuchen33/}} $|$
    \href{https://github.com/utahorange}{\underline{github.com/utahorange}}
\end{center}

%\hrulefill


%-----------EDUCATION-----------------


\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Los Angeles - Computer Science}{2024-2028}
      {Incoming Freshman}{Los Angeles California}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Troy High School}{2020-2024}
      {Troy Tech STEM Program Computer Science, Full International Baccalaureate Diploma, Salutatorian, 1st Decile (top 10 percent GPA)}{Fullerton, CA}
  \resumeSubHeadingListEnd


%-----------Research Interests-----------------	    
\vspace{0pt}
\section{Research Interests}
	Emerging phenomena in 2D Materials, Complex Oxides and Organic-Inorganic Heterostructures; Advanced Spectroscopy Techniques, Synthesis, Growth $\&$ Fabrication of Flexible and Wearable Nanoelectronics Devices.\\

%-----------Awards-----------------
\vspace{0pt}
\section{Awards and Scholarships}
	\begin{description}[font=$\bullet$]
		\item{Best Oral Presentation, $2^{nd}$ Int. Conf. on Physics for Sustainable Development and Technology, 2017, Bangladesh.}
		\vspace{-5pt}
		\item {Dean's List Award, Faculty of Engineering for achieving $CGPA>3.75$ in Junior Year of B.Sc., 2016}
		\vspace{-5pt}
		\item {University Merit Scholarship for outstanding academic results in junior year of B.Sc., 2016}
		\vspace{-5pt}
		\item {$19^{th}$ at ACM – ICPC Semifinal ($9^{th}$ as ICPC Ranklist), Bangladesh Site, 2014.}
		\vspace{-5pt}
		\item {Honorable Mention, Inter University Programming Contest at Daffodil Uni., Bangladesh, 2014}
		%\vspace{-5pt}
		%\item {Government Merit Scholarship for outstanding academic results in higher secondary certificate examinations, 2012}
		
\end{description}

%-----------Publications-----------------
\vspace{-5pt}
\section{Publications}
	\nocite{*}
	\bibliographystyle{unsrt}
	\bibliography{publications}    % 'publications' is the name of a BibTeX file

%-----------Experience-----------------
\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart

        \resumeSubheading
      {Team Captain, Networking and Windows OS Lead}{Aug 2020 - Present}
      {Air Force Association CyberPatriot Competition}{Fullerton, CA}
        \resumeItemListStart
        \resumeItem{Placed 1st nationally out of over 5000 teams and 2nd in Cisco Networking Challenge.}
        \resumeItem{Implemented full connectivity with VLAN, DHCP, NAT, OSPF, ACLs, ZBF, etc to satisfy client requirements.}
        \resumeItem{Secured Cisco IOS devices by configuring a site-to-site VPN with the IPSec network protocol suite.}
        \resumeItem{Maintained Windows services uptime in simulated engagement against active red team, completing business tasks promptly.}
      \resumeItemListEnd
    
\resumeSubHeadingListEnd

%-----------Certifications-----------
\section{Certifications}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{CompTIA Security Plus} \\
     \textit{Issued June 2023 - Expires June 2026} \\
    }}
 \end{itemize}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Cisco Certified Network Associate} \\
     \textit{Issued July 2023 - Expires July 2026} \\
    }}
 \end{itemize}

%-----------Technical Skills-----------------
\vspace{-5pt}
\section{Technical Skills}
	\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Powershell, Python, Java, Cisco IOS, \LaTeX} \\
     %\textbf{Frameworks}{: Selenium/Selenide, Playwright, RestAssured, JUnit, TestNG, Cucumber} \\
     \textbf{Developer Tools}{: Git, Vim} \\
     %\textbf{Libraries}{: WireMock, Spring Cloud Contract, Pact, Chaos Monkey}
    }}
 	\end{itemize}



\end{document}


